\documentclass[10pt]{amsart}

\usepackage{macros,slashed}

\linespread{1.25}

\title{Gauging versus the background field method}

\def\brian{\textcolor{blue}{BW: }\textcolor{blue}}

\begin{document}
\maketitle

\subsection{Gauging = local BRST cohomology}

\brian{recall ordinary BRST cohomology for symplectic actions}

We now explain, in more detail, the process of gauging a symmetry of a BV theory.
We will find that the observables of the gauged theory introduce a ``local" version of BRST cohomology.
In our setup, of course, this will be a factorization algebra. 
As in the case of the equivariant observables, the process of gauging is defined whenever we have a symmetry of a theory by some local Lie algebra, but there are many key differences as we have explained in Table \brian{ref}.
First, we focus on the classical case. 

\subsubsection{}

Indeed, let $\sE$ be the fields of a classical BV theory on a manifold $M$ described by some action functional
\ben
S = S^{free} + I \in \oloc(\sE),
\een
satisfying the classical master equation $\{S, S\} = 0$.
Let $\sL$ be a local Lie algebra that acts on the theory $\sE$ with corresponding Noether functional $I^{\sL} : \sL \to \oloc(\sE)$. 
Recall, this means that the equivariant classical master equation $(\d_{\sL} + Q) (I + I^{\sL}) + \frac{1}{2}\{I + I^{\sL}, I + I^{\sL}\} = 0$, where $\d_{\sL}$ is the Chevalley--Eilenberg differential on $\sL$, is satisfied. 
 
We define a new BV theory built from this action of $\sL$ on $\sE$. 
The space of fields is
\ben
\sE^{\sL}_{BRST} = \sE \oplus \sL[1] \oplus \sL^![-2] .
\een 
The $(-1)$-shifted symplectic pairing is given by the sum of the pairing defining the theory $\sE$ together with the natural pairing
\ben
\<-,-\>_{\sL} : \sL[1] \times \sL^! [-2] \xto{{\rm ev}} {\rm Dens}_M \xto{\int_M} \CC .
\een
The first arrow is the density valued evaluation pairing between $\sL$ and its $!$-dual~$\sL^! = \sL^\vee \tensor {\rm Dens}_M$.
Write $X, X^!$ for elements of $\sL,\sL^!$, respectively. 
The action functional for this new theory is 
\ben
S_{BRST}^{\sL} = S + I^{\sL} + \sum_{n \geq 0} \frac{1}{n!} \<X^!, \ell_n (X, \ldots, X)\>_{\sL} \in \oloc(\sE_{BRST}^{\sL}) . 
\een 
If we denote by $\{\ell_n\}$ the $L_\infty$ structure maps for $\sL$ we can think about this new theory as splitting up into a free part
\ben
S_{BRST}^{\sL, free} = S^{free} + \<X^!, \ell_1(X)\>_{\sL}
\een
and an interacting part
\ben
I_{BRST}^{\sL} = I + I^{\sL} + \sum_{n \ne 1} \<X^!, \ell_n (X,\ldots,X)\>_{\sL} .
\een  

\begin{lem} Let $\{-,-\}_{BRST}$ denote the bracket on $\oloc(\sE^{BRST})$ induced by the $(-1)$-shifted symplectic structure on $\sE^{BRST}$ defined above.
The functional $S^{\sL}_{BRST}$ satisfies the curved classical master equation
\ben
\{S^{\sL}_{BRST}, S^{\sL}_{BRST}\} = \ell_0 .
\een 
\end{lem}

\begin{dfn}
The {\em local BRST complex} for the action of $\sL$ on $\sE$ is the factorization algebra ${\rm Obs}^{cl}_{BRST}$ of classical observables for the theory $(\sE^{\sL}_{BRST}, S^{\sL}_{BRST})$. 
\end{dfn}

The 

\begin{eg}
Suppose that $\Sigma$ is a Riemann surface with fixed metric $g_0$. 
We have already seen in Example \ref{?} how the local Lie algebra controlling deformations of Riemannian metrics $\sL^{Riem}$ acts on the free boson on $\Sigma$. 
The corresponding BRST theory
\ben
\sE_{BRST} = \sE^{boson}_\Sigma \oplus \sL^{Riem}_{(\Sigma,g_0)}[1] \oplus (\sL_{(\Sigma,g_0)}^{Riem})^![-2], 
\een 
is precisely the perturbative expansion of the Polchinski string \ref{?} near the fixed metric $(\Sigma, g_0)$. 
Explicitly, the action functional is \brian{finish, copy from string}
\end{eg}

\begin{eg}
Suppose, again, that $\Sigma$ is a Riemann surface. 
Consider local Lie algebra given by the Dolbeualt complex of holomorphic vector fields $\sL = \sT_\Sigma = \Omega^{0,*}(\Sigma, T_\Sigma^{1,0})$. 
\end{eg}

\subsubsection{}

\brian{Quantum story. Formula in the case that the theory is free.}

\subsection{Examples of BRST cohomology}

\subsection{Chiral gravity}

\end{document}